Trends of SDR in Thessaloniki

### 2023-06-14 Article.Rmd
Commit 2023-06-14 09:17

```{r seasonalALL, echo=F, fig.cap="Trends by season for All-sky condition. Displays monthly means of daily means."}
knitr::include_graphics("./images/SeasonaltTrends-1.pdf")
```

```{r seasonalCLEAR, echo=F, fig.cap="Trends by season for Clear-sky condition. Displays monthly means of daily means."}
knitr::include_graphics("./images/SeasonaltTrends-2.pdf")
```

```{r seasonalCLOUD, echo=F, fig.cap="Trends by season for Cloudy-sky condition. Displays monthly means of daily means."}
knitr::include_graphics("./images/SeasonaltTrends-3.pdf")
```

>>>>

```{r seasonalALL, echo=F, fig.cap="Trends by season for All-sky condition. Displays monthly means of daily means."}
knitr::include_graphics("./images/SeasonalTrends-1.pdf")
```

```{r seasonalCLEAR, echo=F, fig.cap="Trends by season for Clear-sky condition. Displays monthly means of daily means."}
knitr::include_graphics("./images/SeasonalTrends-2.pdf")
```

```{r seasonalCLOUD, echo=F, fig.cap="Trends by season for Cloudy-sky condition. Displays monthly means of daily means."}
knitr::include_graphics("./images/SeasonalTrends-3.pdf")
```
